---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# tsnet

<!-- badges: start -->
<!-- badges: end -->

The goal of tsnet is to include helpful functions for dynamic network modelling in psychology and surrounding fields. Currently, the core of the package is the comparison of Bayesian gVAR models as estimated in the `BGGM` package. 

## Installation

You can install the development version of `tsnet` from [GitHub](https://github.com/bsiepe/tsnet) with:

``` r
# install.packages("devtools")
devtools::install_github("bsiepe/tsnet")
```

## Getting Started

This is a basic example which shows you how to solve a common problem:

```{r example}
library(tsnet)
library(BGGM)

# Load data
data <- BGGM::ifit



```


## References
If you use the package, please cite the preprint that introduces the package and the test: 

Siepe, B.S. & Heck, D.W. (2023). Bayesian Estimation and Comparison of Idiographic Network Models. 
